% Chapter 2

\chapter{Requirement Specification} % Main chapter title

\label{Chapter2} % For referencing the chapter elsewhere, use \ref{Chapter1}

\lhead{Chapter 2. \emph{Requirement Specification}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
\section{Functional Requirements}
Function and features that derives to the end user of the system are following:

\subsection{Affordable Online Presence:} 
Develop a cost-effective solution that enables small businesses to establish and maintain an online platform for their products and services without incurring prohibitive expenses, democratizing access to the digital marketplace.

\subsection{Streamlined Product/Service Integration:} 
Create an automated system leveraging image recognition technology to simplify and expedite the process of adding products and services to the online platform, reducing manual effort and improving efficiency for business owners.

\subsection{Enhanced Customer-Shop Connectivity:} 
Facilitate easy and efficient connection between customers and local shops by providing a user-friendly interface that allows customers to search for products or services based on images, names, or location, thereby fostering a seamless shopping experience.

\subsection{Geolocation Features:} 
Implement geolocation features to enable customers to explore nearby shops and their offerings, aiding in quicker decision-making and fostering a stronger connection between customers and local businesses.

\subsection{Delivery Request Mechanism:} 
Integrate a system that allows customers to request product delivery from the respective sellers, promoting convenience and encouraging increased sales for the shops while enhancing customer satisfaction.

\subsection{Navigation Assistance:} 
Provide navigation features that guide customers to the physical locations of shops, improving accessibility and encouraging more foot traffic to the local businesses, ultimately boosting their visibility and sales.

\subsection{User Experience Optimization:} 
Prioritize an intuitive and appealing user interface and experience to ensure that both sellers and customers find the application easy to use and navigate, enhancing overall satisfaction and encouraging continued usage.

\subsection{Search History Recording:}
Record customer searches to provide a history for their convenience and future reference.

\subsection{Comprehensive Search Results:}
Ensure that search results include a wide array of products, services, and corresponding shops for a complete view of available offerings.

\subsection{Flexible Result Filtering:}
Allow customers to filter search results based on various criteria such as price, ratings, shop proximity, or categories, enabling a personalized and efficient shopping experience.

\subsection{Delivery Requests for Products:}
Implement a mechanism for customers to request product delivery, promoting convenience and seamless transactions.

\subsection{Navigation to Shops:}
Enable customers to obtain directions to the physical shops offering the desired product or service, facilitating a smooth transition from online exploration to in-person shopping.

\subsection{Category-Based Exploration:}
Provide an option for customers to explore products and services based on categories, allowing for effortless browsing without initiating a specific search.



\section{Non-functional Requirements}
Here are the non-functional requirements:

\subsubsection{Performance}
\begin{itemize}
	\item The web application must have rapid response times and load efficiently.
	\item API calls for data fetching and processing should complete within milliseconds for a seamless user experience.
	\item The application should maintain high performance even during peak usage.
\end{itemize}

\subsubsection{User Interface (UI) and User Experience (UX)}
\begin{itemize}
	\item The UI should be intuitive, aesthetically pleasing, and utilize vibrant colors with smooth animations.
	\item The design should be consistent and compatible across various screen sizes and devices.
	\item User interactions and transitions within the application should be smooth and visually appealing.
\end{itemize}

% ... Rest of the non-functional requirements similarly structured ...

\subsubsection{Compatibility}
\begin{itemize}
	\item The web application must be compatible with a wide range of browsers, ensuring consistent functionality and appearance across different platforms.
\end{itemize}

\subsubsection{Scalability}
\begin{itemize}
	\item The architecture should allow for seamless scaling to accommodate a growing user base and increased data load.
	\item The application should be capable of handling increased traffic without compromising performance.
\end{itemize}

\subsubsection{Accessibility}
\begin{itemize}
	\item The application should adhere to accessibility standards to ensure usability for individuals with disabilities.
	\item Content and features should be easily navigable and understandable for users with basic English skills.
\end{itemize}

\subsubsection{Image Storage}
\begin{itemize}
	\item Images should be stored securely in AWS S3 buckets, ensuring data integrity and accessibility.
	\item The image storage system should handle image uploads, retrievals, and deletions in an efficient and organized manner.
\end{itemize}

\subsubsection{Database Management}
\begin{itemize}
	\item The database should be maintained automatically, including regular password changes for enhanced security.
	\item Database operations should be optimized to ensure data retrieval and modification are swift and efficient.
\end{itemize}

\subsubsection{Response Time}
\begin{itemize}
	\item The web application should have minimal loading time, providing near-instantaneous responses to user actions.
\end{itemize}

\subsubsection{Reliability}
\begin{itemize}
	\item The application should operate consistently without frequent crashes or downtimes, ensuring a reliable user experience by instantly report and monitor any bugs or errors, enhancing application reliability.
\end{itemize}



%----------------------------------------------------------------------------------------



