% Chapter 5

\chapter{Conclusion \& Future Work} % Main chapter title

\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1}

\lhead{Chapter 5. \emph{Conclusion \& Future Work}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------

\section{Conclusion}
The "Track My Shop" project introduces a user-friendly and affordable web application tailored for small businesses and local service providers. By offering a centralized platform accessible through standard web browsers on various devices, the project enables businesses to showcase their products and services online. Leveraging image recognition and geolocation features, the application simplifies the process of product listing and enhances the search experience for customers.

The main focus of the project has been to make digitalization affordable and accessible for small businesses. Through a well-structured codebase and an intuitive user interface, the application ensures a seamless and engaging experience for both sellers and customers. The use of modern technologies like Next.js, Ruby on Rails, AWS, and PostgreSQL ensures the application is robust and scalable.

Moving forward, gathering user feedback and staying updated with evolving technologies will be key to refining and improving the application. "Track My Shop" strives to contribute to a more connected digital economy, facilitating a stronger bond between local businesses and their communities.


\section{Future Work}
In the following, we outline the potential areas for future work and enhancements to further improve the "Track My Shop" platform.

\subsection{Enhanced User Experience:}

Conduct usability testing and gather extensive user feedback to refine the user interface, making it even more intuitive and appealing to a broader user base.

\subsection{Machine Learning Integration:}

Explore the integration of machine learning algorithms to enhance the image recognition capabilities, allowing for more accurate and efficient product and service identification from uploaded images.

\subsection{Facial Recognition}
Investigate the possibility of integrating facial recognition technology for profile data completion using profile image and enhanced security within the application.

\subsection{Personalized Recommendations:}

Implement recommendation algorithms based on user preferences and behavior, offering personalized product and service recommendations to customers, thereby enhancing user engagement and sales.

\subsection{Integration of Payment Gateways:}

Incorporate secure and widely used payment gateways to facilitate online transactions directly within the application, streamlining the purchase process for customers.

\subsection{Multi-Language Support:}

Introduce multi-language support to make the application accessible to a more diverse audience, promoting inclusivity and user engagement across different regions and languages.

\subsection{Real-Time Chat and Customer Support:}

Integrate a real-time chat feature to enable direct communication between customers and sellers, fostering better customer support and trust.

\subsection{Inventory Management System:}

Develop an integrated inventory management system for sellers to efficiently track, manage, and update their product and service offerings in real-time.

\subsection{Social Media Integration:}

Integrate social media sharing functionalities to enable users to easily share their favorite products and services with their social network, enhancing the application's reach and user engagement.

\subsection{Third Party Integration for Sign-in:}

Integrate popular third-party authentication services (e.g., Google (for Google My Business), Facebook, Instagram etc.) to allow users to sign in using their existing credentials, enhancing user onboarding and convenience.

\subsection{Integration with Other E-commerce Platforms:}

Investigate the potential for integrating with established e-commerce platforms to allow seamless synchronization of product listings and sales, potentially broadening the reach and opportunities for sellers.

\subsection{Customer Analytics Dashboard:}

Create a comprehensive analytics dashboard for sellers, providing insights into customer behavior, purchase patterns, and popular products, aiding in informed business decisions.

\subsection{Mobile Application Development:}

Extend the project by developing dedicated mobile applications (iOS and Android) to cater to the increasing number of users accessing the platform via mobile devices.

\subsection{Offline Access and Progressive Web App (PWA):}

Implement Progressive Web App features to ensure limited functionality and access to the application even in offline mode, enhancing user experience.

\subsection{Import data from Business Websites:}

Explore features that allow sellers to import or list their existing products or services from already established business websites, streamlining the onboarding process and saving time for sellers.

\subsection{Integration with Local Services:}

Collaborate with local delivery services to enable seamless integration for order deliveries, further enhancing convenience for customers and boosting sales for sellers.
These future directions offer a glimpse into the potential growth and evolution of the "Track My Shop" project, ensuring its continual adaptation to emerging technologies and the evolving needs of both businesses and consumers in the dynamic digital landscape.

